Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-05-31 main_paper.tex
Edit introduction and conclusion to emphasize that the paper is a 'proof of concept'
This is a change that Matias wants and makes sense. I've changed a single paragraph in
the introduction to try to be more upfront about the paper's limitations and I've changed
a few lines in the conclusion.

This bootstrap procedure offers some advantages over analytical methods.  In
particular, both this paper and CCT assume that the observations are generated
independently of each other; however, extending these bias correction methods to
other forms of dependence is relatively straightforward for the bootstrap but
can be substantially more complicated for analytical
corrections, which have to be explicitly derived by the researcher. Similarly,
although we only provide results for the local linear model in this paper, it is
trivial to implement this procedure for higher order polynomials, for
covariate-adjusted estimators (\citealp{frolich2007}, \citealp{calonico2015}),
or for other local smoothers. \citep{loader2006} However, in this paper we focus
on the baseline case of sharp RD with a local linear model and uniform
kernel. Extensions to fuzzy RD designs\footnote{%
  ``Fuzzy'' regression discontinuity design \citep{HTV2001}, as opposed to
  ``sharp'' RD, describes situations where the probability of treatment changes
  discontinuously at a known threshold, but by less than 100\%. Then there are
  treated and untreated subjects above and below the discontinuity but the
  treatment effect remains identified.} %
and nonuniform kernels, which require nontrivial changes to the underlying
bootstrap algorithm, as well as developments to address cross sectional
dependence, are the subject of ongoing research.

@@

This paper proposes a novel bootstrap procedure to obtain robust bias-corrected
confidence intervals in sharp regression discontinuity designs using a uniform
kernel. The approach proposed builds upon the developments and intuition
advanced by CCT and is based on a first-order bias correction. We exploit CCT's
theoretical insight through a new residual bootstrap. In particular, we propose
estimating the local linear model as usual, then estimating a local second order
polynomial and generating bootstrap datasets by resampling the residuals of that
polynomial. This bootstrap allows the bias of the linear model to be estimated
and removed, and the bootstrap can be repeated to accurately estimate the
sampling distribution of the bias-corrected estimator.

Bootstrap procedures are appealing in this setting because they are relatively
easy for applied researchers to modify to account for new and unusual dependence
structures or functional forms. The variance adjustment was proven to be correct
under the assumption of i.i.d.\ data, but could easily be extended to handle
cross-sectional or time series dependence by using the appropriate resampling
strategy on the second order polynomial's residuals. For the analytical methods,
however, new formulas need to be derived to accommodate new features of the
DGP. To fully take advantage of the bootstrap's flexibility, though, these
results need to be extended to other kernels, design strategies (e.g. fuzzy and
kink RD designs) and other more realistic dependence structures. All of these
are the subject of ongoing research.

>>>>

The methods presented in this paper are intended as a ``proof of concept'' that
demonstrates that the analytical correction proposed by CCT can also be
implemented through a new bootstrap procedure. We believe that this procedure is
especially promising because it can allow applied researchers to construct
accurate confidence intervals in settings where unusual forms of dependence
would make it difficult to derive CCT's analytical correction---the dependence
can be accommodates in principle by modifying the resampling algorithm to one
that matches the dependence in the dataset. The specific version of the bootstrap
presented in this paper, however, does not achieve that level of generality yet,
and two limitations should be noted in particular. First, the confidence
intervals produced by this bootstrap depend on two separate bandwidth parameters
that must be generated elsewhere. Since these bandwidths are generated using
analytical methods, the confidence intervals could easily be produced using the
same methods. Second, the bootstrap proposed in this paper imposes local
homoskedasticity and can perform poorly when the DGP exhibits significant
heteroskedasticity. Moreover, in this paper we focus on the baseline case of
sharp RD with a local linear model and uniform kernel. So the practical benefits
of using the bootstrap in this context are relatively limited. Relaxing these
limitations is the subject of ongoing research by the authors.

@@

This paper proposes a novel bootstrap procedure to obtain robust bias-corrected
confidence intervals in sharp regression discontinuity designs using a uniform
kernel. The approach proposed builds upon the developments and intuition
advanced by CCT and is based on a first-order bias correction. We exploit CCT's
theoretical insight through a new residual bootstrap. In particular, we propose
estimating the local linear model as usual, then estimating a local second order
polynomial and generating bootstrap datasets by resampling the residuals of that
polynomial. This bootstrap allows the bias of the linear model to be estimated
and removed, and the bootstrap can be repeated to accurately estimate the
sampling distribution of the bias-corrected estimator. These results demonstrate
that there are bootstrap procedures that can generate asymptotically valid
confidence intervals in the same settings as CCT's. The current implementation
of this bootstrap is very specialized, however, and relaxing its limitations
is the subject of ongoing research.
